Math 462 Project

### 2025-03-12 writing/notes.tex
Add more features to gillespie simulations. Begin writing final code in /models

\begin{itemize}
  \item Basal extracellular Notch ($N$) production has the form $H^{+}(I) = n_{m}I^2/(n_{0}^2 + I^2)$. 
  \item Basal extracellular Delta ($D$) production has the form $H^{-}(I) = d_{m}/(d_{0}^2 + I^2)$.
  \item Extracellular Notch and Delta have the same decay rate, $\gamma$.
\end{itemize}

@@

@@

$$
\begin{aligned}
  \frac{dN}{dt} &= \frac{n_{m}I^2}{n_{0}^2 + I^2} - k_{T}ND_{ext} - \gamma N \\[5pt]
  \frac{dD}{dt} &= \frac{d_{m}}{d_{0}^2 + I^2} - k_{T}DN_{ext} - \gamma D \\[5pt]
  \frac{dI}{dt} &= k_{T}ND_{ext} - \gamma_{I}I
\end{aligned}
$$

@@

$$
\begin{aligned}
  \frac{dN}{dt} &= \frac{n_{m}I^2}{n_{0}^2 + I^2} - (k_{T}D_{ext} + \gamma)N \\[5pt]
  \frac{dD}{dt} &= \frac{d_{m}}{d_{0} + I^2} - (k_{T}N_{ext} + \gamma)D \\[5pt]
  \frac{dI}{dt} &= k_{T}ND_{ext} - \gamma_{I}I \\[5pt]
\end{aligned}
$$

@@

$$
\begin{aligned}
  N &= \frac{1}{\gamma + k_{T}D_{ext}}\left(\frac{n_{m}I^2}{n_{0}^2 + I^2}\right) \\[5pt]
  D &= \frac{1}{\gamma + k_{T}N_{ext}}\left( \frac{d_{m}}{d_{0}^2 + I^2} \right) \\[5pt]
  I &= \frac{k_{T}ND_{ext}}{\gamma_{I}}
\end{aligned}
$$

@@

% $$
% N^{*} = \frac{n_{m}}{2(D_{ext}k_{T} + \gamma)} \pm \sqrt{-\frac{(2D_{ext}\gamma_{I}k_{T}n_{0} - D_{ext}k_{T}n_{m} + 2\gamma \gamma_{I}n_{0})(2 D_{ext} \gamma_{I}k_{T}n_{0} + D_{ext}k_{T}n_{m} + 2\gamma\gamma_{I}n_{0})}{2D_{ext}k_{T}(D_{ext}k_{T} + \gamma)}}
% $$

>>>>

\begin{itemize}
  \item Basal extracellular Notch ($N$) production has the form $H^{+}(I) = n_{m}I^2/(n_{0}^2 + I^2)$. 
  \item Basal extracellular Delta ($D$) production has the form $H^{-}(I) = d_{m}d_{0}^2/(d_{0}^2 + I^2)$.
  \item Extracellular Notch and Delta have the same decay rate, $\gamma$.
\end{itemize}

@@

\subsubsection{Time-Scale Analysis}

The expected time for event $i$ to occur is given by $\mathbb{E}[X_{i}] = 1/\lambda_{i}$. Therefore, the rate at which event $i$ occurs is $\lambda_{i}$, which is equal to the rate at which the event occurs in the original ODE. This means that the trajectories generated from the Gillespie's algorithm implementation of the model can be compared directly to the trajectories generated from the ODE itself, without any need for scaling.

@@

$$
\begin{aligned}
  \frac{dN}{dt} &= \frac{n_{m}I^2}{n_{0}^2 + I^2} - k_{T}ND_{ext} - \gamma N \\[5pt]
  \frac{dD}{dt} &= \frac{d_{m}d_{0}^2}{d_{0}^2 + I^2} - k_{T}DN_{ext} - \gamma D \\[5pt]
  \frac{dI}{dt} &= k_{T}ND_{ext} - \gamma_{I}I
\end{aligned}
$$

@@

$$
\begin{aligned}
  \frac{dN}{dt} &= \frac{n_{m}I^2}{n_{0}^2 + I^2} - (k_{T}D_{ext} + \gamma)N \\[5pt]
  \frac{dD}{dt} &= \frac{d_{m}d_{0}^2}{d_{0}^2 + I^2} - (k_{T}N_{ext} + \gamma)D \\[5pt]
  \frac{dI}{dt} &= k_{T}ND_{ext} - \gamma_{I}I \\[5pt]
\end{aligned}
$$

@@

$$
\begin{aligned}
  N &= \frac{1}{\gamma + k_{T}D_{ext}}\left(\frac{n_{m}I^2}{n_{0}^2 + I^2}\right) \\[5pt]
  D &= \frac{1}{\gamma + k_{T}N_{ext}}\left( \frac{d_{m}d_{0}^2}{d_{0}^2 + I^2} \right) \\[5pt]
  I &= \frac{k_{T}ND_{ext}}{\gamma_{I}}
\end{aligned}
$$

@@
